Methods Power Study

### 2022-08-17 manuscript_draft.Rmd
fix stupid mistake
some mini updates with simulations

```{r import-data}
summary_long <- import("simulation_study/simulated_summary_data.csv")
```

@@

```{r item-figure, echo = F, fig.cap="Add a good caption here."}
summary_long$source <- factor(summary_long$source, 
                              levels = c("Low Variance", "Medium Variance", "High Variance"))

ggplot(summary_long %>% filter(power == 80), aes(original_n, sample_size, color = name)) + 
  geom_point() +  
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  theme_classic() + 
  facet_wrap(~ source*scale2) + 
  xlab("Pilot Sample Size") + 
  ylab("Projected Sample Size") + 
  scale_color_discrete(name = "Cutoff Score")
```

>>>>

```{r import-data}
summary_long <- import("simulation_study/simulated_summary_data_update.csv")

# reorder for graphs
summary_long$source <- factor(summary_long$source, 
                              levels = c("Low Variance", "Medium Variance", "High Variance"))
summary_long$scale2 <- factor(summary_long$scale2, 
                              levels = c("Small Scale", "Medium Scale", "Large Scale"))

# a choice to eliminate the low deciles
summary_long <- summary_long %>% filter(name != "Decile 0" &  name != "Decile 10" & name != "Decile 20")
```

@@

```{r item-figure, echo = F, fig.cap="Add a good caption here."}
ggplot(summary_long %>% filter(power == 80), aes(original_n, sample_size, color = name)) + 
  geom_point() +  
  geom_point(aes(original_n, original_n), color = "black") + 
  geom_line() + 
  theme_classic() + 
  facet_wrap(~ source*scale2) + 
  xlab("Pilot Sample Size") + 
  ylab("Projected Sample Size") + 
  scale_color_discrete(name = "Cutoff Score")
```

### 2022-08-17 simulation_study/simulate_summary.Rmd
some mini updates with simulations

```{r}
sim_mac <- readRDS("simulation_2022-08-14 12:54:44.Rdata")
sim_win
sim_linux

all_sim <- bind_rows(sim_mac, .id = "id")

summary_long <- all_sim %>% 
  group_by(scale, original_n, source, name, power) %>% 
  summarize(sample_size = mean(sample_size),
             value = mean(value), .groups = "keep")
```

@@

```{r}

```

>>>>

```{r eval = F}
sim_mac <- readRDS("simulation_2022-08-15 06:40:46.Rdata")
sim_win <- readRDS("simulation_windows3.Rdata")
sim_linux <- readRDS("simulation_linux4.Rdata")

all_sim <- bind_rows(sim_mac, .id = "id") %>% 
  bind_rows(sim_win, .id = "id") %>% 
  bind_rows(sim_linux, .id = "id")

summary_long <- all_sim %>% 
  group_by(scale, original_n, source, name, power, scale2) %>% 
  summarize(sample_size = mean(sample_size),
            value = mean(value), 
            sd_item = mean(sd_item),
            .groups = "keep",)
```

@@

```{r}
export(summary_long, "simulated_summary_data_update.csv", row.names = F)
```
